---
output: github_document
---
 




<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


```{r, echo = FALSE}
# devtools::install_github("rmhogervorst/badgecreatr")
# badgecreatr::badgeplacer(status = "wip" , githubaccount = "kalimu",githubrepo = "LimeRick")
#[![minimal R version](https://img.shields.io/badge/R>=-3.3.1-6666ff.svg)](https://cran.r-project.org/)
```

 
LimeRick
==========

[![Project Status: active](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/LimeRick)](https://cran.r-project.org/package=LimeRick)
 [![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/LimeRick?)](https://github.com/metacran/cranlogs.app)

<strong>Bridge between R and LimeSurvey</strong>  
by Kamil Wais, Ph. D. ([homepage / contact](http://www.wais.kamil.rzeszow.pl))
 
 
The package homepage:
[http://www.wais.kamil.rzeszow.pl/LimeRick/](http://www.wais.kamil.rzeszow.pl/LimeRick/)

The LimeSurvey homepage:
[http://limesurvey.org](http://limesurvey.org)


## LimeRick: motivation 

* need for a bridge that <span style="font-weight: bold">connects very closely</span> two important open-sorce projects (R&nbsp;and&nbsp;LimeSurvey)
* need for an <span style="font-weight: bold">advanced tool</span> that allow for:
    * <span style="font-weight: bold">quickly importing</span> responses into R from active on-line surveys
    * <span style="font-weight: bold">automatically accessing</span> properties of survey and questions 
    * <span style="font-weight: bold">montoring</span> survey status and responses directly from R
    * <span style="font-weight: bold">adding new responses</span> to a survey directly from R
    * <span style="font-weight: bold">simplifying workflow</span> for reproducible analysis<br> (by providing in advance structured data schema)
    * developing <span style="font-weight: bold">data products</span> based on <span style="font-weight: bold">real-time</span> declarative data collection<br> (ex. continous on-line tracking studies)
    * collecting meta-data of respondents interactions with on-line surveys <br>on <span style="font-weight: bold">unique low-granular level</span>


## LimeRick: tutorial

### Installing developer version from GitHub

```{r, echo=TRUE, eval=FALSE, cache=FALSE}
# install.packages('devtools')
devtools::install_github("kalimu/LimeRick")
```

### Loading the installed package

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
library(LimeRick)
```

### Configuring access to a survey

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# set link to the LimeSurvey API on the demo remote server
options(lsAPIurl = 'http://odgar.pl/survey/index.php/admin/remotecontrol')

# set LimeSurvey user login data for survey testing purposes
options(lsUser = "LimeRickDemo")
options(lsPass = "LimeRickDemo")
```

### Low-level API function calls vs. function wrappers

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# low-level API call
lsAPI(method = "release_session_key")

# API call using a wrapper function
lsSessionKey("release")
```

### Setting a connection to a survey

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# getting session key for the user and saving it inside a special environment
lsSessionKey("set")

# if you work with specific local set it now
Sys.setlocale("LC_ALL", "Polish")
```


### Listing available surveys

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# listing available surveys
(surveyList = lsList("surveys"))

# extracting ID of demo survey
surveyID = surveyList$sid[1] 
```

### Adding responses via on-line survey questionaire

```{r, echo=TRUE, eval=FALSE, cache=FALSE}
# try submit your own answers to the demo survey
browseURL(paste0("http://odgar.pl/survey/index.php/survey/index/sid/", surveyID))
```
or use this link: http://odgar.pl/survey/index.php/survey/index/sid/683736

### Listing survey questions

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
questionList = lsList("questions", surveyID)
```

### Accessing survey or question properites

We can access 22 question properties and 58 survey properties. For example:
```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# Is the survey active? (Y - Yes)
lsGetProperties('survey', surveyID)$active

# What is the main text of a given question?
lsGetProperties('question', surveyID, 16)$question

# Is the question mandatory? (Y - Yes)
lsGetProperties('question', surveyID, 16)$mandatory
```

### Checking survey response

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
lsGetSummary(surveyID)
```

### Importing responses into R

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
d = lsGetResponses(surveyID, completionStatus = 'complete')
tail(d)
```

### Adding responses via R

```{r, echo=TRUE, eval=TRUE, cache=FALSE}
# showing possible options for a particular question
lsGetAnswerOptions(surveyID, questionID = 16)

# specifying a response with the use of question code: surveIDXgroupIDXquestionID
response = list('683736X2X27' = "LimeRick",
                '683736X2X26' = "Adding feedback directly from R",
                '683736X2X16' = "A2",# Academia
                '683736X2X21' = "174" # Poland
                )

# adding the above response 
lsAddResponse(surveyID, response)

# or adding via wrapper function
lsAddFeedback(feedback = "Good job! (Kamil, Poland)", 
              sector = "academia", 
              country = "Poland")
```

## See also:

* LimeSurvey Project Team / Carsten Schmitz (2015). / LimeSurvey: An Open Source survey tool /LimeSurvey Project Hamburg, Germany. URL http://www.limesurvey.org







